\section*{Acknowledgements}

I wish to show my gratitude to my supervisor, Riccardo De Bin, whose guidance and support has been invaluable.

I would like to thank my co-supervisor Nils Lid Hjort. While we did not work much together on this thesis, your influence is as strong as ever.

I wish to express my deepest gratitude to my coauthors. Especially Steffen Grønneberg, the unofficial third advisor of this thesis. It was a pleasure writing the partial identification paper with you and Njål Foldnes! And thanks to Martin Tveten, an excellent partner in \texttt{R}-package development. 

I would also like to thank my colleagues and friends, especially Jonas Christoffer Lindstrøm. We have spent countless hours discussing statistics, often directly influencing this thesis, usually over a couple of beers, and often together with Céline Cunén, whose support I strongly appreciate. Thanks to Emil Stoltenberg for many deep discussions, particularly about Bayesian statistics. Thanks to Vinnie Ko for being an inspiration in getting things done and double-checking some mathematics in the standardized alpha paper. Thanks to Sven Ove Samuelsen for being a pleasant boss and frequently correcting my misconceptions. Thanks to Stephan Michelis, for his encouragement and great comments about the \textit{p}-hacking paper. Thanks to Ørnulf Borgan for his help with thesis-related questions when Riccardo or Nils weren't around. And thanks to my other colleagues and friends at the University of Oslo!

And big thanks to my family for supporting me in my endeavours. Especially my dear wife Kjersti Moss her father Olav Dovland, my mentor in mathematics the last 10 years or so.

Finally, I would like to express my appreciation for the members the causality reading group. We didn't get around to write a paper, but I hope we will in the future.

\vskip\onelineskip
\begin{flushleft}
    \sffamily
    \uiocolon\textbf{\theauthor}
    \\
    Oslo,\MONTH\the\year
\end{flushleft}