\chapter{Supplementary Material for "Partial Identification of Latent Correlations with Binary Data"}
\section*{Description}

\begin{description}
\item[utility.R] Includes functions to compute the bounds from Proposition 1 with normal marginals, bounds from Proposition 2 (Spearman's rho), as well as Spearman's rho of Z when Z is known to have a normal copula.

\item[1.R] Gives basic illustrations of the functions in utility.R by reproduces the empirical examples from the paper.

\item[2.R] Simulates from the extremal distributions (and contains code to plot simulated data from the distributions). Verifies the numerical procedures in the "lcorr"-package via Monte Carlo integration.

\item[3.R] Verifies the numerical procedures in the "lcorr"-package via a brute force numerical integration method.

\item[4.R]  Contains code for the biserial example. Can be extended to other datasets.

\item[5.R]  Contains code for numerical exploration of the bounds as given in the two figures in the appendix.

\item[6.R]  Contains code for approximate the minimum length of the bounds.

\item[plot.R]  Code for the colorful plot in the appendix.
\end{description}
\section*{utility.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/utility.R}
\section*{1.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/1.R}
\section*{2.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/2.R}
\section*{3.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/3.R}
\section*{4.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/4.R}
\section*{5.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/5.R}
\section*{6.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/6.R}
\section*{plot.R}
\lstinputlisting[language=R, breaklines=true, basicstyle=\small]{code/plot.R}
